### 2016-10-03 Paper_Final.tex
Removing some temporary files from package.

In addition to executive particularism, exposure may also be a driver of electoral success. Additional media exposure and the opportunity to hold credit claiming events in concert with spending or legislation may assist cabinet ministers. Evidence suggests that credit claiming is an important part of the ability to capitalize electorally on the delivery of spending or policy goods. (Grimmer, Messing, and Westwood 2012; Bickers, Evans, Stein, and Wrinkle 2007) To the extent that ministers enjoy a differential ability to claim credit, they should reap rewards for doing so.

@@

In Canada, the coefficient on \textit{CabinetNow} is positive and substantively relevant but modest. The confidence interval spans from 1.5\% to 4.8\%. The coefficients suggest that cabinet ministers tend to out-perform comparable non-cabinet minister candidates by 3.1\% on average. To illustrate substantively, 690 contests in the Canadian dataset were decided by margins below 3.1\%, including 45 in the 2015 election. Alternatively, the model suggests that appointment to cabinet is electorally equivalent to three fifths of an extra term served.\footnote{OLS embeds a series of strong modeling assumptions. Model diagnostics validate these assumptions: a QQ plot reveals approximately normal errors; a check for leverage using Cook's distance measures suggest few high-leverage cases and comparable modeling results when excluding these cases; multicollinearity is not present in the data modeled; and heteroskedasticity-robust standard errors are reported.}

@@

Considering these cases in turn: In Canada and New Zealand, nominations are decided by local party offices and are rarely contested, but scandal-ridden or misbehaving incumbents are occasionally denied re-nomination. When an incumbent fails to be renominated, their omission from the dataset causes what amounts to a sampling bias. Incumbents who retire may do so for personal reasons (including family or health reasons, running for local political office, moving to the private sector) or because they credibly fear electoral defeat and would prefer the grace of retirement.\footnote{Incumbents may also retire due to dissatisfaction with office; past work finds this is quite common among all early retirements. (Hall and Van Houweling 1995; Kerby and Blidook 2011) Satisfaction is clearly a return from office, but it is outside the scope of this paper.} Work in the US context, where fundraising for re-election is a full time job, suggests incumbents have an awareness of their future electoral chances, and particularly those dealing with scandal choose to retire rather than lose. (Hibbing 1982; Groseclose and Krehbiel 1994) The exclusion of incumbents who retire due to impending electoral defeat creates sample bias.

>>>>

In addition to executive particularism, exposure may also be a driver of electoral success. Additional media exposure and the opportunity to hold credit claiming events in concert with spending or legislation may assist cabinet ministers. Evidence indicates that credit claiming is an important part of the ability to capitalize electorally on the delivery of spending or policy goods. (Grimmer, Messing, and Westwood 2012; Bickers, Evans, Stein, and Wrinkle 2007) To the extent that ministers enjoy a differential ability to claim credit, they should reap rewards for doing so.

@@

In Canada, the coefficient on \textit{CabinetNow} is positive and substantively relevant but modest. The confidence interval spans from 1.5\% to 4.8\%. The coefficients suggest that cabinet ministers tend to out-perform comparable non-cabinet minister candidates by 3.1\% on average. To illustrate substantively, 690 contests in the Canadian dataset were decided by margins below 3.1\%, including 45 in the 2015 election. Alternatively, appointment to cabinet is electorally equivalent to three fifths of an extra term of tenure.\footnote{OLS embeds a series of strong modeling assumptions. Model diagnostics validate these assumptions: a QQ plot reveals approximately normal errors; a check for leverage using Cook's distance measures suggest few high-leverage cases and comparable modeling results when excluding these cases; multicollinearity is not present in the data modeled; and heteroskedasticity-robust standard errors are reported.}

@@

Considering these cases in turn: In Canada and New Zealand, nominations are decided by local party offices and are rarely contested, but scandal-ridden or misbehaving incumbents are occasionally denied re-nomination. When an incumbent fails to be renominated, their omission from the dataset causes what amounts to a sampling bias. Incumbents who retire may do so for personal reasons (including family or health reasons, running for local political office, moving to the private sector) or because they credibly fear electoral defeat and would prefer the grace of retirement.\footnote{Incumbents may also retire due to dissatisfaction with office; past work finds this is quite common among all early retirements. (Hall and Van Houweling 1995; Kerby and Blidook 2011) Satisfaction is clearly a return from office, but it is outside the scope of this paper.} Work in the US context, where fundraising for re-election is a full time job, demonstrates incumbents have an awareness of their future electoral chances, and particularly those dealing with scandal choose to retire rather than lose. (Hibbing 1982; Groseclose and Krehbiel 1994) The exclusion of incumbents who retire due to impending electoral defeat creates sample bias.
